---
title: "Daily Journal"
author: "N. Harms"
format: 
  html:
    code-link: true
editor: visual
---

"code-link" option includes link to code documentation.

## Libraries

```{r}
library(ggplot2)
library(ggthemes)
```

```{r}
#| eval: false
scale_color_colorblind()
```

## 6/4

-   Collab meeting

## 6/5

-   Started training- Intro-part of module 2

## 6/7

-   Finished module 2 of training

## 6/9

-   Worked on training

## 6/10

-   Finished training

## 6/11

-   Meeting with Susan & Toma at 12
-   Group meeting at 2

## 6/12

-   Worked on write-up

## 6/17

-   Finish up write-up
-   Created a markdown file of WCAG 2.1 AA guidelines (to have a concise easy-access list)

## 6/18

-   Meeting at 2
-   Quarto/Pandoc research
-   Ask Susan about HTML/Quarto/Pandoc/all the things materials

## 6/19

-   Emailed Reka about Help Desk materials

## 6/23

-   Accessibility check on 850 book
-   Notes (started on Part IV: Advanced Topics):
    -   Noticed that the keyboard cannot access the tabs (demonstrating how to run things in R, Python, etc.). Not sure if this is necessary, wanted to mention.
    -   Not accessibility related, but noticed a "nubmers" typo in section 31.3.1 :)
    -   Could perhaps implement a way to skip over the page navigation if so desired (skip to content)
    -   Cannot visibly tell when you're on a code chunk to copy it for some reason

## 6/24

-   fig-alt: adds alt text to figures on output (for accessibility)
-   scale_color_colorblind() from ggplot

## 6/25

-   Group meeting
-   Explore quarto slide (revealjs) features

## 6/27

-   Meeting with Reka

## 6/30

-   

## To-do...

-   Accessibility check for 850 book
    -   Go through WCAG 2.1 Level AA standards (markdown file created)
-   Read up on Quarto: [Mine-Cetinkaya](https://mine-cr.com/about/)
-   Read through [Understanding Techniques for WCAG Success Criteria](https://www.w3.org/TR/2014/NOTE-UNDERSTANDING-WCAG20-20140916/understanding-techniques.html#understanding-techniques)

## Other thoughts...

-   Perhaps create a website with finished materials?
    -   Like slide templates
-   Easy to follow "guidelines" for department use
